Linting Linearity in Core/System FC

### 2022-11-22 proposal.tex
Finish first iteration of proposal introduction

We propose to formalise a type system that is able to type check linear
\emph{Core} at all points in the core pipeline and then to implement it into
GHC. Proposal... \todo{proposal paragraph}

>>>>

Finally, we propose to work and write a master thesis on a formal type system
that is able to accommodate linear programs as seen in Core after optimising
transformations, prove its soundness, and ultimately implement it into GHC's
linter. In concrete, the type system will build on the current linear core
system and add rules based on usage annotations for let, letrec and case
binder bound variables; possibly a new kind of coercion related to
multiplicities, and other rules that might come along.
%
The ultimate measure of success is the -dlinear-core-lint flag that right now,
when enabled, rejects many linearly valid programs in the linter. Ideally, by
the end of our research and implementation, this flag could be enabled by
default and accommodate all existing transformations. Realistically, we want to
formally (in the type system) accept as many diverse transformations as possible
while still preserving linearity, even if we are unable to fix them all.
